Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-19 outputs/paper/paper.Rmd
ggplot

reduced_data %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' race",
       caption = "Figure 2: Distribution of survey respondents' Race") +
  theme(legend.position = "none")

@@

reduced_data %>%
  drop_na(nation_race) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Spending Enough to Improve Conditions of Black Population?",
       caption = "Figure 5: Opinion on National Spending on Improving Conditions of Black Population") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

@@

# reduced_data %>%
#   ggplot(aes(x = gender, fill = gender)) +
#   geom_bar() +
#   scale_fill_brewer(palette = "pink")

@@

reduced_data %>%
  drop_na(nation_welfare) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_welfare)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Spending Enough on Welfare?",
       caption = "Figure 7: Opinion on National Spending on welfare") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(Family_income, 
                                       levels = c("$170,000 or over","$130,000 ~ $169,999","$90,000 ~ $129,999","$60,000 ~ $89,999",
                                                  "$40,000 ~ $59,999","$20,000 ~ $39,999","$10,000 ~ $19,999","Under $10,000")))) +
  geom_bar(position = "dodge") +
  labs(fill = "Family Income") +
  coord_flip()
```

``````{r, echo=FALSE}

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Family_income, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip()

reduced_data %>%
  ggplot(aes(x = nation_education, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = nation_arms, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = Assistance_to_the_poor, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Assistance_to_other_countries, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip() +
  facet_wrap(~born_US)

>>>>

reduced_data %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Race",
       caption = "Figure 2: Distribution of survey respondents' race") +
  theme(legend.position = "none")

@@

reduced_data %>%
  drop_na(nation_race) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Spending Enough to Improve Conditions of Black Population?",
       caption = "Figure 5: Opinion on national spending on improving conditions of black population") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

@@

@@

reduced_data %>%
  drop_na(nation_welfare) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_welfare)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough on Welfare?",
       caption = "Figure 7: Opinion on national spending on welfare") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

reduced_data %>%
  drop_na(degree) %>%
  ggplot(aes(x = degree, fill = factor(Family_income, 
                                       levels = c("$170,000 or over","$130,000 ~ $169,999","$90,000 ~ $129,999","$60,000 ~ $89,999",
                                                  "$40,000 ~ $59,999","$20,000 ~ $39,999","$10,000 ~ $19,999","Under $10,000")))) +
  geom_bar(position = "dodge") +
  labs(fill = "Family Income") +
  coord_flip() +
  facet_wrap(~pres16) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Education, Income and its Effect to the Vote",
       caption = "Figure 8: Distribution of votes by degree and family income")

reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Should the Government Limit Immigration?",
       caption = "Figure 9: Opinion on wheter the US should limit immigration to protect their culture") +
  facet_wrap(~pres16)

reduced_data %>%
  ggplot(aes(x = nation_education, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar(position = "dodge") +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough on Improving Education?",
       caption = "Figure 10: Surveyee's opinion on government's budget on education improvement")

reduced_data %>%
  ggplot(aes(x = nation_arms, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar(position = "dodge") +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough on Arms and National Defense?",
       caption = "Figure 11: Surveyee's opinion on government's budget on arms")

reduced_data %>%
  ggplot(aes(x = Assistance_to_the_poor, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar(position = "dodge") +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Assis the Poor?",
       caption = "Figure 12: Surveyee's opinion on government's budget on assisting the poor")

reduced_data %>%
  ggplot(aes(x = Assistance_to_other_countries, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar(position = "dodge") +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Assis Other Countries?",
       caption = "Figure 13: Surveyee's opinion on government's budget on assisting other countries")
```

# reduced_data %>%
#   ggplot(aes(x = degree, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")

# reduced_data %>%
#   ggplot(aes(x = Family_income, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate") +
#   coord_flip()

@@

@@

@@
